### 2023-05-14 doc/Thesis/chapter/01-introduction.tex
delete unnecessary files and rearange folder structure

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option when becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance is performed with a particle swarm optimization 
algorithm. 
%The resulting optimum is compared with other optimisation methods.

@@

The remainder of this work is organized with chapter 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background information on topics of PV, material science and computational science which were used in this work.
In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimisation in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is one viable option when becoming carbon neutral. 
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search} which harness the whole power output of the sun.
%
One sort of PV are CIGS (copper indium gallium sulfide) cells\cite{Vasekar2010}. 
Due to their large absorption coefficient, less material is needed and they can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple cells are operated in series. 
The cells must be applied to a non-conducting surface.
Glass is a good non-conducting substrate, but very rigid and brittle. 
An alternative is steel, which is ductile, inexpensive and highly available, but conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be synthesised on top.
Polymere would be a obvious choice if not for its low melting point which makes high prodction temperatures inpractical.
A non-toxic material which is suitable for the insulation is \ch{ZrO2}. 
An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel processes often produce porous layers. 
In this work a dense, insulating and homogeneous layer is pursued. 
Machine learning can help to uncover complex non-linear relations, such as the 
dependence of the thickness and resistance of the resulting layer on production factors.
%\td{influence} of the production factors on the thickness and resistance of the resulting layer.
The minimization of the conductance is performed with a particle swarm optimization 
algorithm. 
%The resulting optimum is compared with other optimization methods.

@@

The remainder of this work is organized with chapter 
%\ref{sec:aims} providing insight into the motivation and the goals. Section \ref{sec:theoretical} gives
\ref{sec:theoretical} giving 
some background information on topics of PV, material science and computational science which were used in this work.
In chapter \ref{sec:exp} and \ref{sec:comp} the experimental and computational procedures are described. 
Section \ref{sec:results} is split into three sections: material specific results are presented in section \ref{sec:res-mat}, results regarding particle swarm optimization in section \ref{sec:res-emma} and further analysis in section \ref{sec:res-post-emma}.
Finally, chapter \ref{sec:outlook} summarizes and discusses the outlook and next steps.

### 2023-05-14 doc/Thesis/chapter/05-computational-details.tex
delete unnecessary files and rearange folder structure

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}
A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2
and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
where $C$ took the values 0.05--0.95 with step size 0.05, $\varepsilon$ 0.02--3.8 with 0.2 steps 
and $\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled before each calculation.
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross validation score was calculated. 
The score equals to the coefficient of determination $R^2$ which defined as 
$1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}$.
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
% 
Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

>>>>

\section{Fitting via Machine Learning}
%\td{scarce data may lead to overfitting\cite{Lecun1995conv}}\\
Python 3.10.9 and sci-kit learn 1.1.2\cite{pedregosa2011scikit} were used to implement a linear fit model, \gls{krr} and \gls{svm} with polynomial, \gls{rbf} and sigmoid kernels. 
%\subsection{Grid Search}
A grid search over a set of hyperparameters was executed. 
%https://scikit-learn.org/stable/auto_examples/svm/plot_rbf_parameters.html#sphx-glr-auto-examples-svm-plot-rbf-parameters-py
%https://scikit-learn.org/stable/modules/svm.html#svc
% KRR 
The hyperparameters which were examined in \gls{krr} were kernel, $\gamma_{ml}$ and $\alpha$.
The kernel took the form of \gls{rbf}, sigmoid or polynomial with degree 1--3.
The parameters $\alpha$ and $\gamma_{ml}$ (subscript to distinguish from \textit{optimizand}) took the values 0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2, 5 and 10.
%and 0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, respectively.
Note that $\gamma_{ml}$ is used differently in each kernel. 
% SVM
The kernels for \gls{svm} were the same as for \gls{krr}. 
Further hyper parameters were $C$, $\varepsilon$ and $\gamma_{ml}$, 
where $C$ and $\varepsilon$ took the values 0.05--1 with step size 0.05 %, $\varepsilon$ 0.05--4.0 with 0.2 steps 
and was the same as for \gls{krr} plus \texttt{scale}. %$\gamma_{ml}$ 0.01, 0.05, 0.1, 0.5, 1, 5, 10, and \texttt{scale}. 
Where \texttt{scale} equals to $\frac{1}{d \cdot \sigma(\mathbf{X})}$ with $d$ being the number of features 
and $\sigma(\mathbf{X})$ the variance of the input variables. 
% GRID SEARCH 
The input variables ($c_{zr}$, $\lambda$, $v_{DB}$, $T_{DB}$, $v_{cal}$, $T_{cal}$) 
of the \gls{emma} data set were scaled before each calculation.
% https://scikit-learn.org/stable/modules/generated/sklearn.kernel_ridge.KernelRidge.html#sklearn.kernel_ridge.KernelRidge.score
% https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVR.html#sklearn.svm.SVR.score
For each calculation the 5-fold cross validation score was calculated. 
The score equals to the coefficient of determination $R^2$ which defined the following for non linear regression functions:
\begin{equation}
	\label{eq:r2}
	R^2 = 1-\frac{\sum (y_i - \hat{y}_i)}{\sum (y_i - \bar{y}_i)}
\end{equation}
For each method (\gls{krr} and \gls{svm}) and each \textit{optimizand} ($\gamma$ and $\rho$) 
the parameters with the highest score were noted.
% 
Finally, the different data sets were predicted for each model and \gls{mae} and \gls{mse} were calculated.
These values were also calculated for \gls{emma} and the linear model in order to compare the different methods.

### 2023-05-14 doc/Thesis/chapter/060-results-material.tex
delete unnecessary files and rearange folder structure

In this section the results will pe presented, explained and discussed. 
Starting with physical measurements and material properties. 
Followed by the presentation of the results obtain by optimisation and exploration with the \gls{emma} method. 
Finally, the results of alternative optimisation methods were let loose on the data and compared with the \gls{emma} method.

@@

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and no more used for \gls{db}. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolisation?}.
The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolisation process.
%
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed, instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

@@

%\td{Assumption: Ideally solution evaporate shortly after DB but not before}
%due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualisation

@@

%\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
%after realizing the improved effectiveness of \gls{ipo} for experimentation, 
%it was decided that EMMA will be executed with \gls{ipo} solution.

>>>>

In this section the results will pe presented, explained and discussed. 
Starting with physical measurements and material properties. 
Followed by the presentation of the results obtain by optimization and exploration with the \gls{emma} method. 
Finally, the results of alternative optimization methods were let loose on the data and compared with the \gls{emma} method.

@@

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and no more used for \gls{db}. 
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent (\gls{acoh}) with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by being in contact with "fresh" air in contrast to being sealed. 
It therefore dependent on the water or oxygen in the air corresponding to an oxidation or hyrolization process.
%
Only the introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next time needed, instead of producing a separate solution for each sample.
%
It was discovered that after a \gls{4f} \gls{acoh} solution has aged beyond cloudiness 
the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

@@

%\td{Assumption: Ideally solution evaporate shortly after DB but not before}
%due to the boiling point of \gls{buoh} at 117 C\cite{ncbi1butanol} the room temperature to 80 C were used as temperature during \gls{db}.
%- p76, 146 (10x1F) good, 154 (3x4F) okay, 156 (3x3F) bad visualization

@@

%\td{instead of changing the stabilization agent before optimization, could change after pso, was vor und nachteile?}
%after realizing the improved effectiveness of \gls{ipo} for experimentation, 
%it was decided that EMMA will be executed with \gls{ipo} solution.
